---
bibliography: refs.bib
csl: jamia.csl
fontsize: 10pt
geometry: margin=1in
header-includes:
- \pagenumbering{gobble}
- \renewcommand{\familydefault}{\sfdefault}
- \usepackage{lipsum}
output:
  pdf_document:
    fig_caption: yes
urlcolor: blue
---

```{r setup, include = FALSE}
library(dplyr)
library(ggplot2)
```

\textbf{\Large{A Paper Written in Markdown}}

\textbf{\Large{Jason Rigby$^1$}}

\begingroup\large
$^1$Department of Epidemiology \& Preventive Medicine, Monash University, Melbourne VIC, Australia

Corresponding Author: Jason Rigby, Ph. D., ASPREE Co-ordinating Centre, Department of Epidemiology \& Preventive Medicine, Monash University, 99 Commercial Road, Melbourne, Victoria 3004, Australia (jason.rigby@monash.edu)
\endgroup

## ABSTRACT

\textbf{Objective:} \lipsum[1]\newline
\textbf{Materials and Methods:} \lipsum[1]\newline
\textbf{Results:} \lipsum[1]\newline
\textbf{Discussion:} \lipsum[1]\newline
\textbf{Conclusions:} \lipsum[1]

\textbf{Key words:} write some key words here

\twocolumn

## INTRODUCTION
This is a citation [@Schwartz1970]. These are several citations[@Mandl2012; @Wang2015; @Tamang2015; @Jung2014; @Cure2015]. \lipsum[2]

## METHODS
\lipsum[1] See figure \ref{fig:important-figure}.

![A figure caption \label{fig:important-figure}](figures/graph.dot)

## RESULTS
\lipsum[2-4]

```{r diamonds, echo=FALSE, fig.cap="Diamonds: Price vs Carat \\label{fig:diamonds}"}
ggplot(diamonds,aes(x=carat,y=price,color=cut))+geom_point()
```

See figure \ref{fig:diamonds} for more information.

## DISCUSSION
\lipsum[3-6]

## CONCLUSION
\lipsum[7]

## FUNDING
\lipsum[8]

## ACKNOWLEDGEMENTS
\lipsum[9]

## REFERENCES
